\section{Changes to previous versions}
\subsection{Pending changes for the next release}

\begin{itemize}
\item Public urls for the source code have been changed from a private
GitLab repository to a public GitHub repsoitory.
\item Adds a table of contents to make skimming and navigation easier.
\item Adds this ``change log'' itself. :)
\end{itemize}

\subsection{2015-04-23}
This version was not released.

\begin{itemize}
\item Combine the supplemental appendix with the main document (for
convenience).
\end{itemize}

\subsection{2015-01-09}
This is an incomplete list of the changes made in the `2015-01-09'
version of the paper. This version was resubmitted to
\textit{Econometrica} after the 2013-03-14 version received ``reject
and resubmit.''

\begin{itemize}
\item Moves supporting theoretical results to a supplementary
appendix.
\item Separates the statement of assumptions from the theoretical
results.
\item Replaces the multiple testing results with a much simpler
version.
\item Changes the NED assumptions slightly (the previous version had
an error).
\item Makes several changes to the wording of the paper.
\item Adds an explicit variance-covariance matrix and proves
consistency.
\item Changes the typeface used in the paper and makes other small
changes to the formatting.
\end{itemize}

\subsection{2014-04-01}
\begin{itemize}
\item Removes all of the bootstrap material from the paper to move it
to a separate paper at the request of the \textit{Econometrica}
editor.
\end{itemize}

\subsection{2013-03-14}
First released version of the paper. This version was submitted

%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "mixedwindow"
%%% End: 
